---
title: "Recent Graduate"
author: "Thinh"
date: "8/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up 
```{r}
library(tidyverse)
theme_set(theme_light())
```

```{r cars}
dataset <- tidytuesdayR::tt_load("2018-10-16", 29)
recent_grads <- dataset$`recent-grads` %>% 
  janitor::clean_names() %>% 
  mutate(major = str_to_title(major),
         major = fct_reorder(major, median))

```


# EDA 
## What are the most common majors?


```{r}
recent_grads %>% 
  count(major_category, wt = total, sort = TRUE)
```

What major categories (eg. business, engineering, etc ) were the most common?

```{r}
by_major_category %>% 
  mutate(major_category = fct_reorder(major_category, total)) %>%
  pivot_longer(c(men, women), 
               names_to = "gender",
               values_to = "value") %>% 
  ggplot(aes(major_category, value , fill = gender)) +
  geom_col() + 
  scale_y_continuous(labels = scales::dollar_format()) +
  labs(
    x = "",
    y = "Total # graduate",
    title = "What are the most common major categories?"
  ) + 
  coord_flip() + 
  theme(legend.position = "None")
```

## What category majors make more money than others ? 

```{r}
recent_grads %>%
  ggplot(aes(fct_reorder(major_category, median), median, fill = major_category)) + 
  geom_boxplot() + 
  expand_limits(y = 0) + 
  scale_y_continuous(labels = scales::dollar_format()) + 
  theme(legend.position = "none") + 
  coord_flip()
```

## What are the highest earning majors ? 

```{r}
grads_processing <- recent_grads %>% 
  arrange(desc(median)) %>% 
  select(major, major_category, median, p25th, p75th, sample_size)
```

```{r}
grads_processing %>% 
  filter(sample_size >= 100) %>% 
  head(20) %>% 
  mutate(major = fct_reorder(major, median)) %>% 
  ggplot(aes(major, median, colour = major_category)) + 
  geom_point() +  
  geom_errorbar(aes(ymin = p25th, ymax = p75th)) + 
  expand_limits(y = 0) + 
  scale_y_continuous(labels = scales::dollar_format()) + 
  labs(
    title = "What are the highest-earning major?",
    subtitle = "Top 20 majors with at least 100 graduate surveys",
    y = "Median", 
    x = ""
  ) +
  coord_flip()
```
  

## How does gender breakdown related to typical earnings?

```{r}
recent_grads %>% 
  arrange(desc(total)) %>% 
  head(20) %>% 
  pivot_longer(c(men, women),
               names_to = "gender") %>% 
  mutate(major = fct_reorder(major, total)) %>% 
  ggplot(aes(major, value, fill = gender)) + 
  geom_col() + 
  coord_flip()
```

```{r by_major_category}
by_major_category <- recent_grads %>% 
  group_by(major_category) %>% 
  summarise(across(c(total, men, women), sum, na.rm = TRUE),
            median_salary = sum(median * sample_size) / sum(sample_size)) %>% 
  mutate(share_women = women/total) %>% 
  arrange(desc(share_women))
```



```{r}
library(plotly)

g <- recent_grads %>% 
  mutate(major_category = fct_lump(major_category, 4)) %>% 
  ggplot(aes(share_women, median, label = major_category)) + 
  geom_point(aes(colour = major_category, size = sample_size)) + 
  geom_smooth(method = "lm") + 
  expand_limits(y = 0) +
  scale_x_continuous(labels = scales::percent_format()) + 
  scale_y_continuous(labels = scales::dollar_format())

ggplotly(g)
```

Let's test the hypothesis all major categories

```{r}
recent_grads %>% 
  select(major, total, share_women, sample_size, median) %>% 
  lm(median ~ share_women, data = ., weights = sample_size) %>% 
  broom::tidy()
```


How about within in major categories, the the correlation is still available ?

```{r}
library(broom)

recent_grads %>% 
  select(major, major_category, total, share_women, sample_size, median) %>%
  add_count(major_category) %>% 
  filter(n >= 10) %>% 
  nest(-major_category) %>% 
  mutate(model = map(data, ~ lm(median ~ share_women, data = ., weights = sample_size)), 
         tidied = map(model, tidy)) %>% 
  unnest(tidied) %>% 
  filter(term == "share_women") %>% 
  arrange(estimate) %>% 
  mutate(fdr = p.adjust(p.value, method = "fdr"))
```


# Appendix 

## How big is the sample size we have 

```{r}
grads_processing %>% 
  ggplot(aes(sample_size, median)) + 
  geom_point() + 
  scale_x_log10() + 
  geom_text(aes(label = major), check_overlap = TRUE, hjust = 1, vjust = 1)
```


```{r}
knitr::knit_exit()
```

This is not gonna be run 
```{r}
recent_grads %>%
  group_by(major_category) %>% 
  summarise(median = median(median)) %>% 
  ggplot(aes(fct_reorder(major_category, median), median)) + 
  geom_col() + 
  scale_y_continuous(labels = scales::dollar_format()) + 
  coord_flip() 
```

```{r}
grads_processing %>% 
  filter(sample_size >= 100) %>% 
  tail(20) %>% 
  mutate(major = fct_reorder(major, median)) %>% 
  ggplot(aes(major, median, colour = major_category)) + 
  geom_point() +  
  geom_errorbar(aes(ymin = p25th, ymax = p75th)) + 
  expand_limits(y = 0) + 
  scale_y_continuous(labels = scales::dollar_format()) + 
  coord_flip()
```

