---
title: "Wine Ratings"
author: "Thinh"
date: "9/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Loading the packages 

```{r}
library(tidyverse)
theme_set(theme_light())
```

# Loading the data 
```{r}
tt <- tidytuesdayR::tt_load("2019-05-28")
wine_rating <- tt$`winemag-data-130k-v2` %>% 
  select(-X1)
```

# Cleaning Data & EDA 
```{r}
wine_rating <- wine_rating %>% 
  mutate(year = as.integer(str_extract(title, "20\\d\\d")),
         year = ifelse(year < 2000, NA, year)) %>% 
  filter(!is.na(price))
```

```{r}
wine_rating %>% 
  count(country, sort = TRUE)

wine_rating %>% 
  count(designation, sort = TRUE)

wine_rating %>% 
  count(country, region_1, sort = TRUE)

wine_rating %>% 
  ggplot(aes(year)) +
  geom_histogram()

wine_rating %>% 
  ggplot(aes(points)) + 
  geom_histogram(binwidth = 1)

wine_rating %>% 
  ggplot(aes(price)) + 
  geom_histogram() + 
  scale_x_log10()
```

The distribution of points and price looks like a normal distribution. Let's try to predict with linear regression. 

```{r}
wine_rating %>% ggplot(aes(price, points)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_x_log10()

summary(lm(points ~ log2(price), data = wine_rating))
```

The coefficient is significant. Every time the price double, the expected points goes up by 2.

### What features we can add in the model? 

Have a look on country

```{r}
wine_rating %>% 
  mutate(country = fct_relevel(fct_lump_n(country, 7), "US")) %>% 
  mutate(country = fct_reorder(country, points)) %>% 
  ggplot(aes(country, points)) + 
  geom_boxplot() + 
  coord_flip()
```
The boxplot suggest that the points varies among countries. Try fitting in the model 

```{r}
wine_rating %>% 
  mutate(country = fct_relevel(fct_lump_n(country, 7), "US")) %>% 
  lm(points ~ log2(price) + country, data= .) %>% 
  summary()
```
Slightly reduce RSE


Should we use year as a features in the model? 
```{r}
wine_rating %>% 
  ggplot(aes(year, points, group = year)) +
  geom_boxplot()

wine_rating %>%
  count(year)
```

```{r}
wine_rating %>% 
  mutate(country = fct_relevel(fct_lump_n(country, 7), "US")) %>% 
  lm(points ~ log2(price) + country + year , data= .) %>% 
  summary()
```
The p-value is significant. 

How about taster? 

```{r}
wine_rating %>% 
  mutate(taster_name = fct_relevel(fct_lump_n(taster_name, 6), "Missing")) %>% 
  mutate(taster_name = fct_reorder(taster_name, points)) %>% 
  ggplot(aes(taster_name, points)) + 
  geom_boxplot() + 
  coord_flip()
```

Let's finalise the model 
```{r}
library(broom)
model <- wine_rating %>% 
  replace_na(list(taster_name = "Missing")) %>% 
  mutate(country = fct_relevel(fct_lump_n(country, 7), "US"),
         taster_name = fct_relevel(fct_lump_n(taster_name, 6), "Missing")) %>% 
  lm(points ~ log2(price) + country + year + taster_name , data= .) 

# coefficient plots 
model %>% 
  tidy(conf.int = TRUE) %>% 
  filter(term != "(Intercept)") %>%
  mutate(term = str_replace(term, "country", "Country: "),
         term = str_replace(term, "taster_name", "Taster: "),
         term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(estimate, term, colour = term)) +
  geom_point() + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  labs(
    title = "Coefficient plots",
    x = "Estimate",
    y = ""
  )
```

Coefficient plot suggest all terms are significant

Have a look on how the fitted point versus the actual points

```{r}
augment(model) %>% 
  ggplot(aes(.fitted, points)) +
  geom_point(alpha = .1)

tidy(anova(model)) %>% 
  mutate(sumsq/sum(sumsq))
```

Only a small amount of variance explaied by country, year, taster_name


### Lasso regression on words in description 


Firstly, split words in the description and filter out irrelevant words for the model 
```{r}
library(tidytext)

wine_rating_words <- wine_rating %>% 
  mutate(wine_id = row_number()) %>% 
  unnest_tokens(word, description) %>% 
  anti_join(stop_words, by = "word") %>% 
  filter(!word %in% c("wine", "drink"),
         str_detect(word, '[a-z]'))
``` 

```{r}
wine_rating_words %>% 
  count(word, sort = TRUE) %>% 
  head(20) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(word, n)) + 
  geom_col() + 
  labs(
    title = "Most common words in the description",
    x = "",
    y = "Occurences"
  ) +
  coord_flip()
```

```{r}
library(widyr)

wine_words_filtered <- wine_rating_words %>% 
  distinct(wine_id, word) %>% 
  add_count(word) %>% 
  filter(n >= 100) 

wine_words_filtered %>% 
  pairwise_cor(word , wine_id, sort = TRUE)
```

```{r}
library(Matrix)

wine_word_matrix <- wine_words_filtered %>% 
  cast_sparse(wine_id, word)

wine_ids <- as.integer(rownames(wine_word_matrix))
scores <- wine_rating$points[wine_ids]

library(glmnet)
wine_word_matrix_extra <- cbind(wine_word_matrix, log_price = log2(wine_rating$price[wine_ids]))

glmnet_model <- glmnet(wine_word_matrix_extra, scores)

glmnet_model %>% 
  tidy() %>% 
  filter(term %in% c("rich", "black", "simple", "complex", "vineyard")) %>% 
  ggplot(aes(lambda, estimate, colour = term)) +
  geom_line() + 
  scale_x_log10() + 
  geom_hline(lty = 2, yintercept = 0)


glmnet_model %>% 
  tidy() %>% 
  count(lambda) %>% 
  ggplot(aes(lambda, n)) + 
  geom_line() + 
  scale_x_log10()
```

```{r}
library(doMC)
registerDoMC(cores = 4)
cv_glmnet_model <- cv.glmnet(wine_word_matrix_extra, scores, parallel = TRUE)

 plot(cv_glmnet_model)
```

```{r}
lexicon <- cv_glmnet_model$glmnet.fit %>% 
  tidy() %>% 
  filter(lambda == cv_glmnet_model$lambda.1se,
         term != "(Intercept)") %>% 
  select(word = term, coefficient = estimate)

lexicon %>% 
  arrange(coefficient) %>% 
  group_by(direction = ifelse(coefficient < 0, "Negative", "Positive")) %>% 
  top_n(10, abs(coefficient)) %>% 
  mutate(word = fct_reorder(word, coefficient)) %>% 
  ggplot(aes(word, coefficient, fill = direction)) +
  geom_col() + 
  coord_flip() +
  labs(y = "Estimate the effect of the word on the wine points",
       title = "What words are predictive of a wine's score?")
```

```{r}
wine_rating_words %>% 
  filter(wine_id %in% sample(unique(wine_id), 6)) %>% 
  select(title, word, points) %>% 
  mutate(wine = str_c(str_trunc(title , 40), "(", points, ")")) %>% 
  inner_join(lexicon, by = "word") %>% 
  group_by(title, word) %>% 
  summarise(coefficient = mean(coefficient)) %>% 
  ungroup() %>% 
  mutate(direction = ifelse(coefficient < 0, "Negative", "Positive"),
    word = fct_reorder(word, coefficient)) %>% 
  ggplot(aes(word, coefficient, fill = direction)) + 
  geom_col(show.legend = FALSE) + 
  coord_flip() + 
  facet_wrap(~ title, scales = "free_y") + 
  labs(
    title = "How a lasso regression woud predict each wine's scores",
    subtitle = "Using a lasso regression with an extra term for price",
    x = "",
    y = "Effect on scores"
  )
```


